Analyzing X-ray images in Python with scikit-image

### 2016-08-21 skimage_tomo.tex
Moved numpy paragraph before interpreter paragraph in ecosystem section

The acquisition time of synchrotron tomography images has decreased
dramatically over the last decade, from hours to
seconds \citep{Maire2014}. New modalities such as single-bunch
imaging \citep{Rack2014} provide a time resolution down to the nanosecond
for radiography. However, the time subsequently spent in processing the
images has not decreased as much, so that the outcome of a successful
synchrotron imaging campaign often takes weeks or even months to be
transformed into scientific results.

@@

\em{Caching} provides another tool to speed up data analysis. A situation
that often arises is that, while prototyping a workflow, scripts
(containing the image processing pipeline) are run several times to
experiment with parameters. \texttt{joblib} provides a caching mechanism
that avoids the repetition of function calls, if their arguments have not
changed:
\begin{lstlisting}
>>> from skimage import filters, data
>>> from joblib import Memory
>>> mem = Memory(cachedir='/tmp/joblib')
>>> median = mem.cache(filters.median)
>>> im = data.camera()
>>> filtered_im = median(im, np.ones((3, 3)))
__________________________
[Memory] Calling skimage.filters.rank.generic.median...
median(array([[156, ..., 152],
       ..., 
       [121, ..., 111]], dtype=uint8), array([[ 1.,  1.,  1.],
       [ 1.,  1.,  1.],
       [ 1.,  1.,  1.]]))
__________________________median - 0.0s, 0.0min
>>> filtered_again = median(im, np.ones((3, 3)))
>>> # the above call did not trigger another evaluation
\end{lstlisting}

>>>>

The acquisition time of synchrotron tomography images has decreased
dramatically over the last decade, from hours to
seconds \citep{Maire2014}. New modalities such as single-bunch
imaging \citep{Rack2014} provide a time resolution down to the nanosecond
for radiography. However, the time subsequently spent in processing the
images has not decreased as much, so that the outcome of a successful
synchrotron imaging run often takes weeks or even months to be
transformed into scientific results.

@@

{\em Caching} provides another tool to speed up data analysis. A situation
that often arises is that, while prototyping a workflow, scripts
(containing the image processing pipeline) are run several times to
experiment with parameters. \texttt{joblib} provides a caching mechanism
that avoids the repetition of function calls, if their arguments have not
changed:
\begin{lstlisting}
>>> from skimage import filters, data
>>> from joblib import Memory
>>> mem = Memory(cachedir='/tmp/joblib')
>>> median = mem.cache(filters.median)
>>> im = data.camera()
>>> filtered_im = median(im, np.ones((3, 3)))
__________________________
[Memory] Calling skimage.filters.rank.generic.median...
median(array([[156, ..., 152],
       ..., 
       [121, ..., 111]], dtype=uint8), array([[ 1.,  1.,  1.],
       [ 1.,  1.,  1.],
       [ 1.,  1.,  1.]]))
__________________________median - 0.0s, 0.0min
>>> filtered_again = median(im, np.ones((3, 3)))
>>> # the above call did not trigger another evaluation
\end{lstlisting}
